---
title: "STAT601 Lab3"
author: "Chengen Xie cx22"
date: "February 4, 2015"
output: pdf_document
---

#Exercise 2
##Question 1
```{r}
#### Plot the density ####
xseq <- seq(0,10,0.01)
d.values <- (xseq^4) * (15*exp(-(xseq/2)^5)+(5/81)*exp(-(xseq/6)^5))
plot(xseq,d.values,type = 'l')
```

##Question 2
```{r}
density.function <- function(x){
  return((x^4) * (15*exp(-(x/2)^5)+(5/81)*exp(-(x/6)^5)))
}



samples.uniform <- NULL
N=10000
for ( i in 1:N ) {
  proposal <- runif(1,0,10) # Here we get a proposal value
  density.ratio <- density.function(proposal)/dunif(proposal)  # We calculate the ratio of the densities
  if ( runif(1) < density.ratio ) samples.uniform <- c(samples.uniform,proposal) # If a random uniform is lower than our ratio, we accept our sample, otherwise we reject. Then we repeat this process
}

hist(samples.uniform,freq=FALSE)
print(paste("Acceptance Ratio: ",length(samples.uniform)/N))

```

##Question 3
A good proposal function need to be greater or equal to the distribution that we are going to sample. And also fit the distribution as much as possible.

This desnsity function graph looks close to Gamma(3,2). Therefore I would contruct the density function based on it with adjustments.

```{r}

plot(xseq,density.function(xseq),type="l",col="blue",ylim=c(0,90))
lines(xseq,dgamma(xseq,3.3,0.9),col="red")


M=450
plot(xseq,density.function(xseq),type="l",col="blue",ylim=c(0,100))
lines(xseq,M*dgamma(xseq,3.3,0.9),col="red")
```

##Question 4
```{r}
samples.gamma <- NULL

for ( i in 1:N ) {
  proposal  = rgamma(1,3.3,0.9) 
  density.ratio = density.function(proposal)/(M*dgamma(proposal,3.3,0.9)) 
  if (runif(1) < density.ratio ) samples.gamma<- c(samples.gamma,proposal)
}

hist(samples.gamma,breaks=100)
print(paste("Acceptance Ratio: ",length(samples.gamma)/N))
```

##Question 5
No

#Excercise 3
##Question1
$p(x) = \int\limits_a^x \frac{1}{\int\limits_a^b exp(-\frac{(x-m)^2}{2v}} \exp(-\frac{(x-m)^2}{2v}) dx$

There for it is a truncated normal distribution

##Question2
Using a normal distribution as proposal funtion.

##Question3


The inverse transform sampling method works as follows:

Generate a random number u from the standard uniform distribution in the interval [0,1].
Compute the value x such that F(x) = u.
Take x to be the random number drawn from the distribution described by F.
