---
title: "LAB6"
author: "Chengen Xie (cx22)"
date: "March 5, 2015"
output: pdf_document
---

#Question 1
$$(x y z)^T \sim N((0,0,0)^T,())$$

$$X|Y,Z \sim N(0.899X+0.0101Y,0.1899)$$
$$Y|Z,X \sim N(0.899X+0.0101Z,0.1899)$$
$$Z|Y,X \sim N(0.0526X+0.526Y,0.9895)$$

#Question 2
```{r}
library(mvtnorm)
N <- 1000

x <- rep(0,1,N)
y <- rep(0,1,N)
z <- rep(0,1,N)



for(i in 2:N){
  x[i] <- rnorm(1,0.899*y[i-1] + 0.0101*z[i-1],0.1899)
  y[i] <- rnorm(1,0.899*x[i-1] + 0.0101*z[i-1],.1899)
  z[i] <- rnorm(1,0.0526*x[i-1] + 0.0526*y[i-1],0.9895)
}

xseq <- seq(1:N)
plot(xseq,x,type='l')
```

The sample is not mixed enough and always concertrating on a certain point.

#Question 3
```{r}
x <- rep(0,1,N)
y <- rep(0,1,N)
z <- rep(0,1,N)


for(i in 2:N){
  a <- rmvnorm(1, c(0.1,0.1)*z[i-1],matrix(c(0.99,0.89,0.89,0.99),nrow=2, ncol=2))
  x[i] <- a[1]
  y[i] <- a[2]
  z[i] <- rnorm(1,0.0526*x[i-1] + 0.0526*y[i-1],0.9895)  
}

xseq <- seq(1:N)
plot(xseq,x,type='l')
```


The sample is distributed much more uniformly and does not wandering on a certain point

#Question 4
The performence of the second Gibbs sampling is much better. Because using normal sampling there the x y will be related. Updating simultaneously using block samplingwill improve the independency between samples.Therefore increase the performance.

